On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-06 tt_theorem.tex
Thm 5 minor fix

\begin{theorem}[$\delta= 1, \alpha=2$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 2$.
It can yield an infinite structure, but the transcript folds into the zig-zag conformation after its ($27n^2 + 9n +1$)-th bead.
\end{theorem}

\begin{proof}
 We assume $w[i]$ is the first bead stabilized outside $\hexagon^n_O$.
 See Fig.~\ref{fig:ttt_d2}.
 The next bead $w[i+1]$ is to be bound for stabilization.
 Hence, it goes to the west  or to the east (Fig.~\ref{fig:ttt_d2}).
 Once $w[i+2]$ is stabilized at $p$, the remaining transcript folds into the zig-zag conformation.
 In order to avoid this or nondeterminism, $w[i+2]$ must form two bonds; it thus decreases binding capability by 1.
 Until when a bead is stabilized outside $\hexagon^{n+1}_O$, binding capability never increases because of arity being 2 and of the Tunnel Troll Theorem.
 This means that, only at most $\#bc(C_0) \leq 2n$ times we can thus expand that hexagonal region.
 In other words, outside $\hexagon^{3n}_O$ the transcript cannot help but fold into the zig-zag conformation. \qed

>>>>

\begin{theorem}[$\delta= 1, \alpha=2$]
Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 2$.
It can yield an infinite structure, but the transcript folds into the zig-zag conformation after its $(27n^2 + 9n +1)$-th bead.
\end{theorem}

\begin{proof}
 We assume $w[i]$ is the first bead stabilized outside $\hexagon^n_O$.
 See Fig.~\ref{fig:ttt_d2}.
 The next bead $w[i+1]$ is to be bound for stabilization.
 Hence, it goes to the west  or to the east (Fig.~\ref{fig:ttt_d2}).
 Once $w[i+2]$ is stabilized at $p$, the remaining transcript folds into the zig-zag conformation.
 In order to avoid this or nondeterminism, $w[i+2]$ must form two bonds; it thus decreases binding capability by 1.
 Until when a bead is stabilized outside $\hexagon^{n+1}_O$, binding capability never increases because of arity being 2 and of the Tunnel Troll Theorem.
 This means that, only at most $\#bc(C_0) \leq 2n$ times we can thus expand that hexagonal region.
 In other words, outside $\hexagon^{3n}_O$ the transcript cannot help but fold zig-zag. \qed
